---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
library(devtools)
load_all()
```

# README

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/rsizem2/example-rpackage-fars.svg?branch=master)](https://travis-ci.com/rsizem2/example-rpackage-fars)
<!-- badges: end -->

The `fars` package provides several functions for analyzing vehicle crash data. The original code was provided as part of the *Building R Packages* course on Coursera. This original code was been edited to avoid using some deprecated functions and provide more cross-platform functionality.

## The FARS datasets

The FARS data comes from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. The data for the years 2013, 2014 and 2015 are included with this package in the `extdata` directory.

## Installation

You can install this package directly from GitHub using the `devtools` package:

``` {r, eval = FALSE}
library(devtools)
install_github("rsizem2/example-rpackage-fars")
```

## Example

We can visualize the accident data for a given state if we know the state number. For example, the state code for Kentucky is 21, so we can generate the accidents in the year 2015 as follows:

```{r, fig.align='center'}
fars_map_state(state.num = 21, year = '2015')
```

The state code for Alabama is 1, so the accidents in 2013 can be generated with the following code:

```{r, fig.align='center'}
fars_map_state(1,'2013')
```



