---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
library(devtools)
library(magrittr)
load_all()
```

# fars

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/rsizem2/example-rpackage-fars.svg?branch=master)](https://travis-ci.com/rsizem2/example-rpackage-fars)
<!-- badges: end -->

The `fars` package consists of sample R code for analyzing vehicle crash data. The code was provided as part of the *Building R Packages* course on Cousera. 

## The FARS datasets

Describe FARS data...

## Installation

You can install this package directly from GitHub using the `devtools` package:

``` {r, eval = FALSE}
library(devtools)
install_github("rsizem2/example-rpackage-fars")
```

## Example

We can visualize the accident data for a given state if we know the state number. For example, the state code for Kentucky is 21, so we can generate the accidents in the year 2015 as follows:

```{r, fig.align='center'}
fars_map_state(state.num = 21, year = '2015')
```

The state code for Alabama is 1, so the accidents in 2013 can be generated with the following code:

```{r, fig.align='center'}
fars_map_state(1,'2013')
```



